Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-07 RET_Hosts.tex

To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models.

@@

Due to the redshift rangeTo begin, we determine a set of indicators for which to calculate abundances for our DES RET sample. For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}. For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04). At abundances around $12 + \log mathrm{O/H} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio. In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII / \OII ratio \citep{Kewley2008}. In the cases where \NII is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy mass to derive a crude metallicity estimate from the MZR of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic. For $12 + \log mathrm{O/H}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.

To

We recalculate the metallicities given in \citet{Kruehler2015} using the M13 calibration.

>>>>

To estimate the physical properties of the host galaxies, we generate synthetic photometry in the DES $griz$ bands by combining the individual SEDs of simple stellar population models. We use \citet{Bruzual2003} models and a \citet{Chabrier2003} initial mass function (IMF). From the synthetic spectra we derive model magnitudes in the DES $griz$ bands and compare them to the observed magnitudes. For each set of model and observed magnitudes we calculate a $\chi^2$ value and adopt the $M/L$ and SFR from model with the lowest $\chi^2$ as our best estimates. To estimate uncertainties, we interpolate between the next best fitting models and take the values at the 16th and 84th percentiles to be our $1\sigma$ lower and upper bounds.

@@

Due to the redshift range of our sample, and the limited wavelength coverage of the spectra ($3000-8000~\AA$), we are unable to use a single line ratio to estimate the oxygen abundances. We thus determine a set of indicators for which to calculate abundances. For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}. For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04). At abundances around $12 + \log mathrm{O/H} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio. In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII / \OII ratio \citep{Kewley2008}. In the cases where \NII is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy mass to derive a crude metallicity estimate from the MZR of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic. For $12 + \log mathrm{O/H}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the scale of PP04 (O3N2) using the conversion from \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted average of the values after transforming them to the PP04 O3N2 scale.
